Updated Criteria for the Diagnostic Procedure for Parkinson’s Disease Dementia on Level I and their Validity in Deep Brain Stimulation Cohort

### 2025-04-11 texts/theart.qmd
Adding citations

A comprehensive neuropsychological battery was administered in accordance with the Level II criteria for Parkinson's Disease Mild Cognitive Impairment (PD-MCI), as outlined by the MDS Task Force [@litvan2012]. The methodology, including the use of a regression-based normative scoring approach, has been detailed in a prior study [@bezdicek2017]. The neuropsychological assessment covered five cognitive domains, each evaluated through specific tests as follows: **attention and working memory**: assessed using Trail Making Test Part A (TMT-A) [@reitan2004], Prague Stroop Test – Dots (PST-D) [@bezdicek2021], Letter Number Sequencing (LNS) [@wechsler1997], WAIS Digit Span Backward (WAIS DSB) [@wechsler1997], and WAIS Corsi Block Backward (WAIS CB) [@wechsler1997]; **executive Function**: evaluated via the Tower of London (ToL) [@specific1982], Categorical Verbal Fluency (CF) [@benton1989], Trail Making Test Part B (TMT-B) [@reitan2004], subtests from the Prague Stroop Test – Words (PST-W) and Colors (PST-C) [@bezdicek2021]; **language**: measured with the WAIS Similarities subtest [@wechsler1997] and the Boston Naming Test (BNT-60) [@kaplan1983]; **memory**: examined using the Rey Auditory Verbal Learning Test (RAVLT) [@rey1964] for immediate and delayed recall (including List B and recognition trials), and the Brief Visual Memory Test–Revised (BVMTR) [@benedict1997], including delayed recall and forced choice recognition; **Visuospatial Function**: assessed through the Judgment of Line Orientation Test (JoLO) [@benton1983], Clock Drawing Test (CLOX) [@royall1998], and the Grooved Pegboard Test (GPT) [@klove1963].

>>>>

A comprehensive neuropsychological battery was administered in accordance with the Level II criteria for Parkinson's Disease Mild Cognitive Impairment (PD-MCI), as outlined by the MDS Task Force [@litvan2012]. The methodology, including the use of a regression-based normative scoring approach, has been detailed in a prior study [@bezdicek2017]. The neuropsychological assessment covered five cognitive domains, each evaluated through specific tests as follows: attention and working memory assessed using Trail Making Test Part A (TMT-A) [@bezdicek2012; @reitan2004], Prague Stroop Test – Dots (PST-D) [@bezdicek2021], Letter Number Sequencing (LNS) [@wechsler1997], WAIS Digit Span Backward (WAIS DSB) [@wechsler1997], and WAIS Corsi Block Backward (WAIS CB) [@wechsler1997]; executive function evaluated via the Tower of London (ToL) [@specific1982], Categorical Verbal Fluency (CF) [@benton1989], Trail Making Test Part B (TMT-B) [@reitan2004], subtests from the Prague Stroop Test – Words (PST-W) and Colors (PST-C) [@bezdicek2021]; language measured with the WAIS Similarities subtest [@wechsler1997] and the Boston Naming Test (BNT-60) [@kaplan1983]; memory examined using the Rey Auditory Verbal Learning Test (RAVLT) [@frydrychova2018; @rey1964] for immediate and delayed recall (including List B and recognition trials), and the Brief Visual Memory Test–Revised (BVMTR) [@havlík2020; @benedict1997], including delayed recall and forced choice recognition; visuospatial function assessed through the Judgment of Line Orientation Test (JoLO) [@benton1983], Clock Drawing Test (CLOX) [@royall1998], and the Grooved Pegboard Test (GPT) [@klove1963].
